\section{Solutions}
During the early stages of the project we began searching for existing solution to draw inspiration to the design and implementation phases. all members of the group have previously had experience using different recipe sites on the Internet, and we all think that the different site lacks functionality. But good ideas and can be drawn from different solutions and we will in this section review and discuss these existing solutions.  

\subsection*{Supercook}
The best searching recipe website we found is called supercook.com\cite{supercook}. We like this website because you can search for recipes by ingredients, this can be on a single ingredient or multiple. The search-bar also gives helps the user auto-complete ingredients, for faster and less error prone typing. 
The user is only able to enter ingredients in the search-bar, meaning it is not possible to do a free-text search on the recipe you already know. The website's use is to discover or find recipes with already bought ingredients, or ingredients you plan to buy. The website search uses a very simple method for finding recipes, normally it get the good result, but its sorting of results is weird. The sorting algorithm sorts the results in what you have all the ingredients for highest, which can result in some unwanted recipes. \todo{explain the cloud, and the searching method}

\subsection*{Allthecooks}
Allthecooks recipes is one of the most downloaded\todo{cite this from the app store-website} Android application that is related to food and cooking. The application has a great design, it is intuitive and easy to navigate. The detailed display of a recipe is especially well implemented, the user has everything on a single activity, and can easily see the needed ingredients and the steps to cook the recipe. The user can also by a press of a button calculate between different measuring units, or add the selected ingredient to a shopping list.


We want to make it easier for the user to find the correct recipe.


