One in every five people in the world today own a smartphone\cite{peoplesmartphones}, and their popularity among consumers does not seem to decline\citep{mobilegrow}. Mobile devices allow for easy access to the Internet at all times, which means easier access to a vast amount of information and different kinds of media outside of your home, this includes music, video, and books.

The online media is becoming a good alternative to physical media since it is a lot easier to search for it on your phone or computer which you always have near you. 
For example it is a lot easier to buy or rent an e-book online with a few clicks on your device than having to go to the library and borrow it. 
This means that in some cases books are becoming obsolete, among that are cookbooks. 
A physical cookbook is not going to be replaced purely by online recipes but the online recipes allow people to easily and fast search for recipes without having to borrow or buy a cookbook.

Cookbooks provide a static set of recipes, whereas a mobile device can provide you with a vast amount of recipes. Depending on the size of the device/cookbook, it might be easier to read from a mobile device and more convenient to move it around in the kitchen. A mobile cookbook can also provide a way to search for recipes and easily bookmark recipes you like.

A mobile cookbook provides the option to search for recipes when you want it. You can search for recipes while you are in the supermarket in order to find out which ingredients you need for a specific dish. This means you do not need to plan ahead of your grocery shopping as much. Thus mobile devices allow for a way to assist you in impulse visits to the supermarket.
