After a small preview of the already existing solutions, of both web and android applications. We believe that we can create an application with improved features, such as a better search algorithms, with easy navigation, and an elegant design. We like the idea of being able to search for recipes by ingredients, but we wont exclude the possibility to also search directly for recipes. We will also provide the user with different input styles; text-type-input(free text for recipe search and ingredient restricted), and tile-input. Tile input is basically the same as ingredient restricted input, but instead of typing the name of each ingredient the user selects the ingredient by use of tiles. The ingredient are divided into categories and maybe even subcategories, to make the navigation more sensible, otherwise the user would be presented with too many tiles and the screen would be cluttered.

Finding recipes for cooking online has been become easy with the vast amount of sites that offer them. This has also extended to the mobile platform, allowing the users to quickly find a recipe wherever they are. It is very easy to type in the recipe you want to make and it comes up with a list of ingredients and a step by step guide on how to cook the dish.

The user does not always know exactly what dish they want to cook, but instead know which ingredients they have or what ingredients they want to use.

Being able to search for recipes based on ingredients the user already has allows them to customise their searching and receive a larger selection of dishes. It allows them to search based on items they already have in their kitchen, or based on items they know are about to go bad and they need to use. The user could also be in a situation where they see something on sale at the supermarket and quickly need to find out what dishes they can make using this ingredient.

With these problems in mind we have come up with the following problem statement for our project:

\begin{quote}
How can we take advantage of the mobile platform, in order to provide the user with relevant recipes based on specific ingredients, and taking any user defined restrictions into consideration.
\end{quote}