\section{Requirements}\label{sec:requirement}

Based on the research of existing solutions and our problem definition, we have come up with a list of requirements for our application. This list can be seen in this section.

\begin{enumerate}
  \item\label{req:android} \textbf{Android} \\
    The application must be able to run on Android version 4.3 and newer.
    
  \item\label{req:ingredientsearch} \textbf{Search by ingredients} \\
    The user must be able to search for recipes containing specific ingredients defined by the user.
    
  \item\label{req:recipesearch} \textbf{Free-text search} \\
    The user must be able to search for a recipe by its title.
    
  \item\label{req:searchfilters} \textbf{Search filters} \\
    The different search methods must support filtering for users that might be allergic to certain ingredients.
    
  \item\label{req:favourite} \textbf{Favourite recipes} \\
    The user must be able to save their favourite recipes. They must also be able to remove recipes from their favourite list.
    
  \item\label{req:shoppinglist} \textbf{Shopping list} \\
    The user must be able to add and remove ingredients from a shopping list directly from the recipe. They must also be able to add and remove ingredients directly from the shopping list as well.
    
  \item\label{req:sharing} \textbf{Sharing} \\
    The user must be able to share recipes and shopping lists with other users using Facebook, Google+, E-mail, and SMS.
    
  \item\label{req:persistency} \textbf{Persistency} \\
    The system must be able to keep the user's shopping list and favourite recipes persistent.
    
  \item\label{req:unitconversion} \textbf{Unit conversion} \\
    The application must support unit conversion between the imperial system and the metric system.
    
  \item\label{req:additionallanguages} \textbf{Additional languages} \\
    The system must be ready for internationalisation.
  
  \item\label{req:Nologinrequired} \textbf{No login required} \\
    The user should not be required to log in, to use the application. Though the user might not be able to use certain features if not logged in.
\end{enumerate}