\section{Stories}
The following section we create user stories as the basis for finding how the users navigate through our application. The stories are made up and they are trying to cover all the key navigation paths in the application\todo{The idea with the user stories was to explain how end users might be navigating through the application, however should the stories be up before requirements?}

\subsubsection*{Julie}

Julie is at the supermarket, she does not know what to have for dinner later. She sees that minced beef is on sale, but she does not know what recipes include this. She opens the application \appname. She is presented with a page that says "Click above to search for ingredients". She clicks the button, and a view of categories appears at the bottom of the screen. She clicks the category called "Meat", and a word cloud appears with many different kinds of meat. In the word cloud she finds minced beef and clicks it. She now a press the back button and the application performs a search presents Julie with recipes which uses minced beef. The top results include recipes such as Spaghetti Bolognese and Lasagne. Having not thought about this before, Julie wants to cook Spaghetti Bolognese for dinner. She opens the recipe and can now see all the ingredients she need for this recipe. Remembering which of the ingredients she has at home, she then adds the ingredients she needs to her shopping list. Then she favourites the recipe to easily find it later. Julie opens her shopping list and continues shopping.

\subsection*{Bob}
Bob is at home, he does not know what to have for dinner later. He looks in the fridge because there might be something to use. In the fridge he finds some chicken which has a best before date set to today. To get some inspiration he opens the application and types in chicken and a few other ingredients he has in the kitchen. The application provides him with several recipes including chicken, he decides he wants Chicken Tikka Masala. Based on the ingredients he typed in before he discovers that he is missing paprika. He adds paprika to his shopping list and favourites the recipe. His wife Sofie has not arrived at home yet, so instead of going to the supermarket himself, he decides to share his shopping list with Sofie.

\subsection*{Alice}
Alice is at home, earlier she found a Lasagne recipe and she has already bought all the ingredients for it. She opens the something else application \appname, goes to the favourites page, and opens her previously favourited recipe for Lasagne. In the recipe she scrolls down to the instructions and follows these in order to make her dinner.
