\documentclass[a4paper,12pt]{memoir}
\usepackage{framed}
\usepackage{enumitem}
\usepackage{todonotes}

%Commands
\newcommand{\testdesign}[4]
{
\begin{framed}
\begin{description}
\item \textbf{Identifier:} #1
\item \textbf{Features to be tested:} #2
\item \textbf{Approach:} #3
%\item \textbf{Test case identification:} #4
\item \textbf{Pass/fail criteria:} #4
\end{description}
\end{framed}
}

\title{Miniproject in Test and Verification - Part 1}
\author{Jacob Karsten Wortmann\\Sam Sepstrup Olesen\\Nicklas Andersen}

\begin{document}
\maketitle
\chapter*{Miniproject}
%project description
We will in our project make an application that functions as an digital cookbook. The user are able to search for recipes by different search functions, by ingredients, and by the name of the recipe. User can share the recipes with friends or relatives, it is also possible to favourite a recipe. Our application supports conversion between the imperial and metric system, to reach a larger audience.

\section*{1a - Test Design}
%The purpose of the test design spec is to organize and describe the testing that needs to be performed on a specific feature. It doesn’t, however, give the detailed cases or the steps to execute to perform the testing.
\section{Technical specification}
\begin{description}
    \item[Server-side]
        We will use PHP5.x to do the server-side scripting,
        we will perform unit test with the tool PHPUnit and mutation test with judgedim/Mutagenesis.
    \item[Client-side]
        We will use android SDK x to develop the Android application and use the Android Testing Framework to perform unit tests.
\end{description}

%test description and plan
We want to perform unit test on both the client-side and server-side.\\
unit test:\\
Create a copy of the database and test different functions such as: creation of a recipe, query and display a recipe, deletion of a recipe, edit recipe, comment on a recipe.\\
Change of language, 

%add an recipe to the database 
\testdesign
{ServerTest01} %identifier
{Create a complete recipe, with picture, ingredients, and instructions} %features to be testet
{Take a recipe from a normal cookbook, and add it to the application's database.} %approach
{A pass is when all test cases are run without finding a bug} %pass&fail criteria

%testdesign that tests calculation between metric and imperial system.
\testdesign
{ServerTest02} %identifier
{} %features to be testet
{} %approach
{} %pass&fail criteria

%testdesign that tests if the application changes accordingly when user changes the language.
\testdesign
{ServerTest03} %identifier
{} %features to be testet
{} %approach
{} %pass&fail criteria

%testdesign der vil tjekke om det insatte data også er ens med det der kommer ud igen på selve applicationen.
\testdesign
{AppTest01} %identifier
{Reciving data from the server} %features to be testet
{Recieve a recipe from the server and test whether it is the correct data.} %approach
{The data received should the same data as sent from the server.} %pass&fail criteria
\end{document}